Tropical Andes IUCN Montane and Lowland forest

### 2023-07-31 code/L0/L0_TropicalAndes_IUCNhabitatClassification.Rmd
convert to sf save shapefile

>>>>

# Convert to sf
```{r}
TA_iucn_habitat_forest_shape <- rasterToPolygons(TA_iucn_habitat_forest, na.rm = TRUE, dissolve = TRUE)
```

```{r}
plot(TA_iucn_habitat_forest_shape)
```

# Save shapefile
```{r}
shapefile(TA_iucn_habitat_forest_shape, filename = file.path(output_path, "TropicalAndes_IUCNHabitat_Forest.shp"), overwrite=TRUE)
```
